Testing atlantisom: generate census length comps

### 2019-05-08 TrueLengthCompTest.Rmd
try a survey census

```{r calcage2length-truth}

@@

This produces output. Visualize:

@@

# for an example species, by polygon, layer because this is full resolution

@@

So the question now is, do we run `create_survey` on the output of this, or do we `create_survey` on all three truth components first, then run `calc_age2length` to get a survey sample? This should work and will eliminate the unsampled areas/times/species.

>>>>

```{r calcage2length-truth, warning=FALSE, message=FALSE, eval=FALSE}

@@

This produces output, after a looooooong time. Its doing it for all species, which is a problem. Visualize a tiny bit:

@@

# for an example species, by polygon, layer because this is full resolution
# everyone's favorite predator

atf_length_census <- length_census$natlength %>%
  filter(species %in% ("Arrowtooth_flounder"))

@@

So the question now is, do we run `create_survey` on the output of this, or do we `create_survey` on all three truth components first, then run `calc_age2length` to get a survey sample? The latter should work and will eliminate the unsampled areas/times/species.

It should save time to run the census survey to get true length comps, because at least it aggregates over polygon and layer. Test this:

```{r censussurvey-calcage2length, warning=FALSE, message=FALSE}

survey_testresnall <- create_survey(dat = truth$resn,
                                 time = timeall, # use timeall? yes to match Nall
                                 species = survspp,
                                 boxes = boxall,
                                 effic = effic1,
                                 selex = selex1)

survey_teststructnall <- create_survey(dat = truth$structn,
                                 time = timeall, # use timeall? yes to match Nall
                                 species = survspp,
                                 boxes = boxall,
                                 effic = effic1,
                                 selex = selex1)

# survey_testNall with truth$nums as dat was created above

length_censussurv <- calc_age2length(structn = survey_teststructnall,
                                 resn = survey_testresnall,
                                 nums = survey_testNall,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)
